R Notebook

### 2019-04-02 notebooks/paper_L123_results_section.Rmd
got rid of leftover macro and fixed compile error, also some new code

Step 4. Translate to L3?
What is L3?
We want class info and attribute info, on some level.
Let's do classes first.
```{r}
# get rid of classes we have dealt with.
los <- lapply(los, function(lof) lapply(lof, class_to_primitive_df))
```

@@

All the numbers are low, so there's no clear pattern, which makes sense.
How best to incorporate this...
```{r}

>>>>

Step 4: Translate to L1+.

In L1+, we will collapse some obviously collapsible distinctions (e.g., reals).
```{r}
los <- lapply(los, function(s) lapply(s, fold_NULL_and_NA_into_other_types_df))

los <- lapply(los, function(lof) {lapply(lof, function(df) {change_type_systems_df(df, type_map_sv_to_real)})})

los <- lapply(los, function(lofuns) {lapply(lofuns, combine_scalar_vector_where_appropriate)})

null_na_fold_real_arg_counts <- build_arg_count_df_from_lopkgs(los)
null_na_fold_real_fun_counts <- build_fun_count_df_from_lopkgs(los)
```

TODO oops scalar vector thing.

Write counts.
```{r}
xtable(null_na_fold_real_arg_counts) %>% print(include.rownames=F)
xtable(null_na_fold_real_fun_counts) %>% print(include.rownames=F)
```

Breakdown by argument signature.
```{r}
poly_type_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_type_args))
poly_type_args <- poly_type_args[order(-poly_type_args$count),] # sort by count
poly_type_args$perc <- round(poly_type_args$count/sum(poly_type_args$count) * 100, 2)
```

Print top 10.
```{r}
format_df_for_print(poly_type_args[1:10,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

Step 5. Translate to L3?
What is L3?
We want class info and attribute info, on some level.
Let's do classes first.
```{r}
# get rid of classes we have dealt with.
los <- lapply(los, function(lof) lapply(lof, class_to_primitive_df))
```

@@

All the numbers are low, so there's no clear pattern, which makes sense.
How best to incorporate this...
```{r}
xtable(L3_c_basic_df) %>% print(include.rownames=F)
```

```{r}
format_df_for_print(L3_poly_class_args[1:10,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

Let's find out when class is monomorphic and type is polymorphic.
```{r}
num_poly_type_not_poly_class <- apply_count_to_lopkg_c(los, args_count_all_poly_type_mono_class)
```

Are there patterns?
```{r}
lo_pt_mc <- reduce_extracted_lopkgs_to_one_new(apply_extract_to_lopkg(los, extract_poly_type_args_w_mono_class))
lo_pt_mc <- lo_pt_mc[order(-lo_pt_mc$count),] # sort by count
lo_pt_mc$perc <- round(lo_pt_mc$count/sum(lo_pt_mc$count) * 100, 2)

format_df_for_print_new(lo_pt_mc[1:10,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

How about attributes?
```{r}
los_a <- lapply(los, function(lofun) lapply(lofun, function(df) convert_df_attr_to_ts(df, type_map_T0_to_r)))

L3_poly_attr_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los_a, extract_poly_attr_args))
L3_poly_attr_args <- L3_poly_attr_args[order(-L3_poly_attr_args$count),] # sort by count
L3_poly_attr_args$perc <- round(L3_poly_attr_args$count/sum(L3_poly_attr_args$count) * 100, 2)

format_df_for_print_new(L3_poly_attr_args[1:10,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```
